---
title: "JO_bios524_finalproject"
output: html_document
date: "2023-10-04"
---
```{r}
library(readr)
library(dplyr)

library(ggplot2)
library(tidyverse)

```


```{r}

EV <- read.csv("C:/Users/joi/OneDrive/Desktop/Biomedical Computing/Electric_Vehicle_Population_Data.csv")

Vehicle <- EV %>% select (Make, Model) %>% arrange(Make, Model)

name_of_make <- unique(Vehicle$Make)
name_of_make


name_of_model <- unique(Vehicle$Model)
name_of_model


vehicle <- EV %>% arrange(Model)
```

```{r}
bios524final::myplot(vehicle, Model)


 
```

```{r}

factor_Model <- as.factor(EV$Model)
factor_Model <- as.numeric(factor_Model)
EV <- cbind(EV, factor_Model)

cor(factor_Model, EV$Base.MSRP )
````

MSRP <- EV %>% filter( Base.MSRP != 0 ) %>%
  select(c(County, City, Model.Year, Make, Model, Base.MSRP, Electric.Vehicle.Type)) %>% 
   arrange(desc(Base.MSRP))


freq_MSRP<- MSRP %>% filter( Base.MSRP != 0 ) %>%
  arrange(Make, Model)


freq_MSRP_hist <- MSRP %>% filter( Base.MSRP != 0 ) %>%
  arrange(Make, Model) %>%
  ggplot(aes(x = Base.MSRP)) + 
  geom_histogram()

freq_MSRP_hist



freq_MSRP_hist + xlim(0, 50000)

# Price is usually between (30000, 50000) and EV is expensive.
freq_MSRP_hist + xlim(30000, 50000)


freq_MSRP_hist + xlim(50000, 200000)


freq_MSRP_hist + xlim(500000, 1000000)



```
